\bf Title here

### 2020-06-22 paper/paper.tex
Comments/questions added for discussion on Wed 24 June

% !TeX program = pdfLaTeX
\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{textcomp}
\usepackage[hyphens]{url} % not crucial - just used below for the URL
\usepackage{hyperref}
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

@@

@@

@@

\begin{figure}
\includegraphics[width=1\linewidth,height=0.6\textheight]{/Users/hzha400/Documents/3.PhD/paper-tour-vis/figures/tour_path_increasing} \caption{\label{tour-path}An illustration of the tour path}\label{fig:tour-path}
\end{figure}

@@

@@

\hypertarget{visual-diagnostics}{%
\subsection{Visual diagnostics}\label{visual-diagnostics}}

@@

@@

>>>>

% !TeX program = pdfLaTeX
\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{textcomp}
\usepackage[hyphens]{url} % not crucial - just used below for the URL
\usepackage{hyperref}
\usepackage{todonotes}
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

@@

In an optimization problem the goal is to find the best solution
within the space of all feasible solutions which typically is represented
by a set of constraints. The problem consists on optimizing an objective
function $f: S \rightarrow \Re$ with $S \in \Re^n$ in a reduced spaced given
by the problem constraints to either minimize or maximize a function.... Gradient based
optimization has been typically used to solve such problems.
However, there are many situations where derivatives
of an objective function are unavailable or unreliable and therefore
traditional methods based on derivatives are not the best option to solve an optimization problem....
\todo[inline]{Intro to optimization to set the scene for the paper?}

@@

\todo[inline]{How about adding more details into derivative free methods?}

@@

%\begin{figure}
% \includegraphics[width=1\linewidth,height=0.6\textheight]{/Users/hzha400/paper-tour-vis/figures/tour_path_increasing} \caption{\label{tour-path}An illustration of the tour path}\label{fig:tour-path}
\todo[inline]{I commented out the figure: Can you please update the path above to be a relative path instead?Thanks!}
%\end{figure}

@@

\todo[inline]{Are we using  projection pursuit/guided tour to better understand
the convergency of optimization algorithms visually in combination with the
algorithms discussed below? Or we are focusing on the optimisation problem
only within the project pursuit context? Some of the problems listed below
are also applicable to optimization problem in general too }

@@

\todo[inline]{I would expland this section more as the core contribution}
\hypertarget{visual-diagnostics}{%
\subsection{Visual diagnostics}\label{visual-diagnostics}}

@@

\todo[inline]{I would add the maths here to describe the
simulations}

@@

\todo[inline]{I was wondering if it would be worth to talk
with a bit more detail about the tour for the audience that might
not be familiar with it?}
